The great codivergence bake off

### 2025-11-26 manuscript/ms.tex
Updating plots of empirical results.

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-all-pairs/pyco-sumevents-mediterranean-all-pairs-pycoevolity-nevents-cropped.pdf}
        \caption{
            \Ecoevolity results for all Mediterranean pairs.
        }
        \label{fig:neventsmediall}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-soil-pairs/pyco-sumevents-mediterranean-soil-pairs-pycoevolity-nevents-cropped.pdf}
        \caption{
            \Ecoevolity results for soil Mediterranean pairs.
        }
        \label{fig:neventsmedisoil}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-all-pairs/pyco-sumevents-philippines-all-pairs-pycoevolity-nevents-cropped.pdf}
        \caption{
            \Ecoevolity results for all Philippines pairs.
        }
        \label{fig:neventsphilall}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-negros-panay-pairs/pyco-sumevents-philippines-negros-panay-pairs-pycoevolity-nevents-cropped.pdf}
        \caption{
            \Ecoevolity results for Negros-Panay pairs.
        }
        \label{fig:neventsphilnp}
    \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-all-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
        \caption{
            Results comparison for all Mediterranean pairs.
        }
        \label{fig:neventsmediall}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-soil-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
        \caption{
            Results comparison for soil Mediterranean pairs.
        }
        \label{fig:neventsmedisoil}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-all-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
        \caption{
            Results comparison for all Philippines pairs.
        }
        \label{fig:neventsphilall}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-negros-panay-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
        \caption{
            Results comparison for Negros-Panay pairs.
        }
        \label{fig:neventsphilnp}
    \end{center}
\end{figure}
